---
title: "Basic Inference Analysis Part 2/2"
author: "Ameen AboDabash"
date: "May 29, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
##loading requrired packages
packages<-c("datasets","ggplot2")
sapply(packages, require, character.only = TRUE)
## setting the seed, to insure this analysis will end up with the same results
set.seed(1982)
```



###Part 2
####Objectives:
1- Provide a basic summary of the data.

2- Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.

3- State your conclusions and the assumptions needed for your conclusions.


So, lets load and summarize the thooth growth data:
 
 
####Data Summary
```{r}

data(ToothGrowth)

summary(ToothGrowth)

head(ToothGrowth)


 
plot <- ggplot(ToothGrowth, 
               aes(x=factor(dose),y=len,fill=factor(dose)))
plot + geom_boxplot(notch=F) + facet_grid(.~supp) +
     scale_x_discrete("Dosage") +   
     scale_y_continuous("Length of Teeth") +  
     ggtitle("Effect of Dosage and Supplement on Tooth Growth")

 
```

####confidence intervals



```{R}

supp.t1 <- t.test(len~supp, paired=F, var.equal=T, data=ToothGrowth)
supp.t2 <- t.test(len~supp, paired=F, var.equal=F, data=ToothGrowth)
supp.result <- data.frame("p-value"=c(supp.t1$p.value, supp.t2$p.value),
                          "Conf-Low"=c(supp.t1$conf[1],supp.t2$conf[1]),
                          "Conf-High"=c(supp.t1$conf[2],supp.t2$conf[2]),
                          row.names=c("Equal Var","Unequal Var"))
supp.result
```




####Conclusion :
The supplement (OJ) appears to provide better results than the supplementing with VC.


Part1 & 2 all on [github]<https://github.com/aabodabash/BasicInferenceAnalysis.git>
